---
output:
  rmarkdown::github_document
bibliography: "inst/references.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# R/`SuperNOVA`

<!-- badges: start -->
[![R-CMD-check](https://github.com/blind-contours/SuperNOVA/workflows/R-CMD-check/badge.svg)](https://github.com/blind-contours/SuperNOVA/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/blind-contours/SuperNOVA/master.svg)](https://codecov.io/github/blind-contours/SuperNOVA?branch=master)
[![CRAN](https://www.r-pkg.org/badges/version/SupernOVA)](https://www.r-pkg.org/pkg/SuperNOVA)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/SuperNOVA)](https://CRAN.R-project.org/package=SuperNOVA)
[![CRAN total downloads](http://cranlogs.r-pkg.org/badges/grand-total/SuperNOVA)](https://CRAN.R-project.org/package=SuperNOVA)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![MIT license](https://img.shields.io/badge/license-MIT-brightgreen.svg)](https://opensource.org/licenses/MIT)
<!-- [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4070042.svg)](https://doi.org/10.5281/zenodo.4070042) -->
<!-- [![DOI](https://joss.theoj.org/papers/10.21105/joss.02447/status.svg)](https://doi.org/10.21105/joss.02447) -->
<!-- badges: end -->

> Efficient Estimation of the Causal Effects of Non-Parametric Interactions and Effect Modifications using Stochastic Interventions
__Authors:__ [David McCoy](https://davidmccoy.org)

---

## What's `SuperNOVA`?

The `SuperNOVA` R package is designed to provide facilities to data-adaptively identify 
variable sets that are most predictive of an outcome of interest and construct
efficient estimators for the counterfactual mean of an outcome under
stochastic interventions on these variables. Stochastic interventions are shifts
to the exposures that depend on the naturally observed values
[@diaz2012population; @haneuse2013estimation]. `SuperNOVA` builds off of the `txshift` 
package which implements the targeted maximum likelihood (TML) estimator
of a stochastic shift causal parameter originally proposed by @diaz2018stochastic. `SuperNOVA` extends 
the original stochastic intervention methodology from one treatment/exposure variable to include
joint stochastic interventions on two variables which allows for the construction of a non-parametric
interaction parameter. Likewise, `SuperNOVA` also estimates both individual stochastic intervention outcomes
under some delta shift compared to outcome under no intervention and a target parameter for effect modification which
is the difference in mean outcomes under intervention compared to no intervention across strata of an effect modifier. 

Of course, it is not known a priori in most cases what variables are interacting or modifying effects and 
therefore it is necessary to identify these variable sets first. As such `SuperNOVA` uses V-fold cross-validation framework to estimate a data-adaptive parameter in training folds and a non-parametric interaction target parameter in estimation folds. Our data-adaptive parameters are variable sets used in basis functions in the best fitting multivariate adaptive regression spline model. The best fitting model is determined using a Super Learner which selects the model from an ensemble with the lowest cross-validated MSE. Variable sets are considered important based on ANOVA-like variance decompositions for the basis functions in the best fitting model. Individual variables and variable sets used in all the training folds are considered consistent predictors. The interaction target parameter is applied to variable sets composed of two variables in the mixed exposure. This target parameter is the expected outcome under a dual shift of both variables by some delta compared to the sum of individual shifts. Other parameters exist for effect modification and individual variable shifts. Cross-validated targeted minimum loss-based estimation (TMLE) is used to update the initial expected outcomes given stochastic shift interventions.  This method, called SuperNOVA, guarantees consistency, efficiency, and multiple robustness. SuperNOVA provides researchers with V-fold specific and pooled results for each target parameter. Additional information is provided in the vignette. 

`SuperNOVA` integrates with the [`sl3`
package](https://github.com/tlverse/sl3) [@coyle-sl3-rpkg] to allow for ensemble
machine learning to be leveraged in the estimation procedure for each nuisance parameter 
and estimation of the data-adaptive parameters in the iterative backfitting procedure used to identify basis functions in the best fittin model. There are several stacks of machine learning algorithms used that are constructed from `sl3`. 

---

## Installation

For standard use, we recommend installing the package from
[CRAN](https://CRAN.R-project.org/package=SuperNOVA) via

```{r cran-installation, eval = FALSE}
install.packages("SuperNOVA")
```

_Note:_ If `SuperNOVA` is installed from
[CRAN](https://CRAN.R-project.org/package=SuperNOVA), the `sl3`, an enhancing
dependency that allows ensemble machine learning to be used for nuisance
parameter estimation, won't be included. We highly recommend additionally     
installing `sl3` from GitHub via
[`remotes`](https://CRAN.R-project.org/package=remotes):

```{r sl3-gh-master-installation, eval = FALSE}
remotes::install_github("tlverse/sl3@devel")
```

For the latest features, install the most recent _stable version_  of `SuperNOVA`
from GitHub via [`remotes`](https://CRAN.R-project.org/package=remotes):

```{r gh-master-installation, eval = FALSE}
remotes::install_github("blind-contours/SuperNOVA@main")
```

To contribute, install the _development version_ of `SuperNOVA` from GitHub via
[`remotes`](https://CRAN.R-project.org/package=remotes):

```{r gh-devel-installation, eval = FALSE}
remotes::install_github("blind-contours/SuperNOVA@devel")
```

---

## Example

To illustrate how `SuperNOVA` may be used to ascertain the effect of a mixed exposure, consider the following example:

```{r example, warning=FALSE}
library(SuperNOVA)
library(devtools)
load_all('~/sl3')
set.seed(429153)
# simulate simple data
n_obs <- 400
```


The `simulate_data` function creates simulated data with a multivariate exposure, covariates (confounders), and a continuous outcome.
```{r simulate data, eval = TRUE}
data_info <- simulate_data(n_obs = n_obs)
data <- data_info$data
head(data)
```

```{r setup learner stacks}

## this is the stack of learners to learn the density of our exposures, or the g mechanism
sl_density_lrnr <- make_density_superlearner()

# this stack will be used to find basis functions in the mixture during an iterative backfitting procedure, details in vignette
Lrnr_earth_1 <- Lrnr_earth$new(linpreds = FALSE, degree = 1)
Lrnr_earth_2 <- Lrnr_earth$new(linpreds = FALSE, degree = 2)
Lrnr_earth_3 <- Lrnr_earth$new(linpreds = FALSE, degree = 2, pmethod = "none")

learners <- c(
  Lrnr_earth_1,
  Lrnr_earth_2,
  Lrnr_earth_3
)

names(learners) <- c(
  "full earth 1",
  "full earth 2",
  "full earth 3"
)

Exposures_stack <- make_learner(Stack, learners)

## this is the stack of learners used to estimate Y given covariates in the iterative backfitting procedure

Lrnr_glm_basic <- Lrnr_glm$new()
Lrnr_mean_base <- Lrnr_mean$new()

Lrnr_ridge <- Lrnr_glmnet$new(alpha = 0)
Lrnr_lasso <- Lrnr_glmnet$new(alpha = 1)

learners <- c(
  Lrnr_earth_1,
  Lrnr_earth_2,
  Lrnr_earth_3,
  Lrnr_glm_basic,
  Lrnr_mean_base,
  Lrnr_ridge,
  Lrnr_lasso
)

names(learners) <- c(
  "full earth 1",
  "full earth 2",
  "full earth 3",
  "Lrnr_glm",
  "Lrnr_mean",
  "Lrnr_ridge",
  "Lrnr_lasso"
)

Covariate_stack <- make_learner(Stack, learners)

## and now we make the estimators for our Q or outcome mechanism: 

mean_lrnr <- Lrnr_mean$new()
fglm_lrnr <- Lrnr_glm_fast$new()
rf_lrnr <- Lrnr_ranger$new()
lasso_learner <- Lrnr_glmnet$new(alpha = 1)
ridge_learner <- Lrnr_glmnet$new(alpha = 0)
lrn_polspline <- Lrnr_polspline$new()
lrn_ranger100 <- make_learner(Lrnr_ranger, num.trees = 100)
hal_lrnr <- Lrnr_hal9001$new(max_degree = 3, n_folds = 3)

Outcome_stack <- make_learner(
  Stack, mean_lrnr, fglm_lrnr, rf_lrnr, lasso_learner, ridge_learner, lrn_polspline, lrn_ranger100, Lrnr_earth_1, Lrnr_earth_2, Lrnr_earth_3
)

```




```{r run SuperNOVA, eval = TRUE}
W <- data[, c("W2", "W3")]
A <- data[, c("M1", "M2", "M3")]
V <- data[, c("W1")]
Y <- data[, c("Y")]


sim_results <- SuperNOVA(W = W,
                         V = V,
                         A = A,
                         Y = Y,
                         delta = 1,
                         LOD_val = 0,
                         Density_stack = sl_density_lrnr,
                         Exposures_stack = Exposures_stack,
                         Covariate_stack = Covariate_stack,
                         Outcome_stack = Outcome_stack,
                         n_folds = 3,
                         family = "continuous",
                         quantile_thresh = 0) 

indiv_shift_results <- sim_results$`Indiv Shift Results`
em_results <- sim_results$`Effect Mod Results`
joint_shift_results <- sim_results$`Joint Shift Results`
```

Let's first look at the results for individual stochastic shifts by delta compared to no shift:

```{r individual shift results}
indiv_shift_results
```

Next we can look at effect modifications: 

```{r effect modification results}
em_results
```

And finally results for the joint shift

```{r joint results}
joint_shift_results
```
---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/nhejazi/SuperNOVA/issues). Further details on filing
issues are provided in our [contribution
guidelines](https://github.com/nhejazi/SuperNOVA/blob/master/CONTRIBUTING.md).

---

## Contributions

Contributions are very welcome. Interested contributors should consult our
[contribution
guidelines](https://github.com/nhejazi/SuperNOVA/blob/master/CONTRIBUTING.md)
prior to submitting a pull request.

---

## Citation

After using the `SuperNOVA` R package, please cite the following:

        @article{hejazi2020efficient,
          author = {Hejazi, Nima S and {van der Laan}, Mark J and Janes, Holly
            E and Gilbert, Peter B and Benkeser, David C},
          title = {Efficient nonparametric inference on the effects of
            stochastic interventions under two-phase sampling, with
            applications to vaccine efficacy trials},
          year = {2020},
          doi = {10.1111/biom.13375},
          url = {https://doi.org/10.1111/biom.13375},
          journal = {Biometrics},
          publisher = {Wiley Online Library}
        }

        @article{hejazi2020SuperNOVA-joss,
          author = {Hejazi, Nima S and Benkeser, David C},
          title = {{SuperNOVA}: Efficient estimation of the causal effects of
            stochastic interventions in {R}},
          year  = {2020},
          doi = {10.21105/joss.02447},
          url = {https://doi.org/10.21105/joss.02447},
          journal = {Journal of Open Source Software},
          publisher = {The Open Journal}
        }

        @software{hejazi2022SuperNOVA-rpkg,
          author = {Hejazi, Nima S and Benkeser, David C},
          title = {{SuperNOVA}: Efficient Estimation of the Causal Effects of
            Stochastic Interventions},
          year  = {2022},
          doi = {10.5281/zenodo.4070042},
          url = {https://CRAN.R-project.org/package=SuperNOVA},
          note = {R package version 0.3.7}
        }

---

## Related

* [R/`tmle3shift`](https://github.com/tlverse/tmle3shift) - An R package
  providing an independent implementation of the same core routines for the TML
  estimation procedure and statistical methodology as is made available here,
  through reliance on a unified interface for Targeted Learning provided by the
  [`tmle3`](https://github.com/tlverse/tmle3) engine of the [`tlverse`
  ecosystem](https://github.com/tlverse).

* [R/`medshift`](https://github.com/nhejazi/medshift) - An R package providing
  facilities to estimate the causal effect of stochastic treatment regimes in
  the mediation setting, including classical (IPW) and augmented double robust
  (one-step) estimators. This is an implementation of the methodology explored
  by @diaz2020causal.

* [R/`haldensify`](https://github.com/nhejazi/haldensify) - A minimal package
  for estimating the conditional density treatment mechanism component of this
  parameter based on using the [highly adaptive
  lasso](https://github.com/tlverse/hal9001) [@coyle-hal9001-rpkg;
  @hejazi2020hal9001-joss] in combination with a pooled hazard regression. This
  package implements a variant of the approach advocated by @diaz2011super.

---

## Funding

The development of this software was supported in part through grants from the
National Library of Medicine (award no. [T32
LM012417](https://reporter.nih.gov/project-details/9248418)) and the National
Institute of Allergy and Infectious Diseases (award no.  [R01
AI074345](https://reporter.nih.gov/project-details/9926564)) of the National
Institutes of Health, as well as by the National Science Foundation (award no.
[DMS 2102840](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2102840)).

---

## License

&copy; 2017-2022 [Nima S. Hejazi](https://nimahejazi.org)

The contents of this repository are distributed under the MIT license. See below
for details:
```
MIT License
Copyright (c) 2017-2022 Nima S. Hejazi
Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:
The above copyright notice and this permission notice shall be included in all
copies or substantial portions of the Software.
THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
SOFTWARE.
```

---

## References
